Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-06 Paper/paper.tex
Figure generation, workon first part of the apper

\usepackage{color}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

@@

\newcommand{\toolname}{{\color{blue}TOOL\_NAME }}

@@

\begin{document}
\maketitle
\begin{multicols}{2}

  \section{Abstract}

  Internet topology has been measured and modeled for many years, but few studies  quantify how the topology changes over time.  Over the past decade, governments around the world have recognized that the Internet is a powerful tool for controlling and surveilling their citizens, and they have begun enacting common policies for ASes operating within their borders.

  In this paper, we ask how AS topology has changed over time with respect to national boundaries.  We introduce a new measure, \emph{chokepoint potential}, to characterize how a country's AS topology is organized in terms of paths that can carry traffic across international borders.  To study country-level chokepoints, we developed \toolname, a suite of open source, cross platform, and efficient tools for monitoring national chokepoints on the AS graph.  To illustrate these ideas and tools, we studied how chokepoint potential correlates with two independent measures of civilian liberty, finding [NEED A RESULT HERE].  [NEED A RESULT FOR WHAT WE FOUND FOR EVOLUTION OVER TIME].

This paper extends earlier research on AS topology and BGP simulation to study chokepoints across the Internet over multiple years, using our
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years. We provide comprehensive and accessible tools for studying
the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible.

@@

\par Widespread Internet censorship and surveillance pose a
significant threat to individuals throughout the world. As routine
tasks, communications, entertainment, and information move on-line and
are mediated by the Internet, most of us have little choice about
whether or not to rely on the Internet.  According to the
International Telecommunication Union (ITU), the number of individual
Internet users increased from 1.024 million in 2005 to 3.578 million
in 2017 \cite{itu}. The majority of these users operate in an
environment that restricts Internet freedom in some way. For example,
the 2017 Freedom on the Net report from Freedom House reports that
64\% of Internet users belong to a nation with Internet that is not
free or partly free \cite{FOTN}.  Beyond censorship and surveillance,
the EU is considering content rules surrounding copyright, net
neutrality rules in the U.S. were recently overturned, and large
content delivery networks are under enormous pressure to 'do
something' about fake news and bad actors. Taken together, these
trends will likely restructure the Internet in unforeseen ways,
as organizations respond to new challenges and realities.

Today, most such control is exercised at the country level,
as governments have recognized both the threat and the opportunity
that is posed by ubiquitous on-line communication. For example, much
of the organization, revolutionary momentum, and broadcasting of
events during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}, and similarly several countries
sought to control these movements by disconnecting in-country networks from the rest of the world (FIXME: need references here).

These two factors, increasing levels of content monitoring and
Internet dependence, point to the need for improved tools and methods
for studying worldwide Internet censorship and surveillance over time.
[A SENTENC OR TWO HERE SUMMARIZING THE STATE OF THE FIELD AND WHAT'S
  MISSING.]  In this paper, we focus on AS-level topology and on
censorship, asking how AS topology has changed over time with respect
to national boundaries.  We define \emph{chokepoint potential} to
quantify how a country’s AS topology is organized in terms of paths
that can carry traffic across international borders.  We developed a
suite of tools, called \toolname, for studying national chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how chokepoint potential correlates with two independent
measures of civilian liberty, finding [NEED A RESULT HERE]. [NEED A
  RESULT FOR WHAT WE FOUND FOR EVOLU- TION OVER TIME].

@@

% Major Contributions
\par
The primary contributions of our work are as follows: \textbf{1.} We introduce the measure of chokepoint potential and 
motivate its value as way to interpret the capability for a nation to enact censorship of its Internet traffic. \textbf{2.} We
provide an overview of the evolution of national AS-level chokepoints over time, showing the evolution of the Internet
allowing for a comparision between nations. \textbf{3.} We develop a new tool, \toolname, that provides the capability for
efficiently evaluating chokepoints for a given state of the Internet. Finally, \textbf{4.}, we show that our chokepoint measure
has a significant relationship to Internet freedom as measured by a qualitative source.

>>>>

\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{geometry}
\usepackage{todonotes}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

@@

\newcommand{\toolname}{{\textcolor{blue}TOOL\_NAME }}
\newcommand{\Ben}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}

@@

\begin{document}
\maketitle
\begin{multicols}{2}
\abstract{
  Internet topology has been measured and modeled for many years, but few studies  quantify how the topology changes over time.\Ben[inline]{This is not true, there are many studies of the evolution of the AS Internet. We should be more specificy about what this statement means, ie with respect to national boundaries}.  Over the past decade, governments around the world have recognized that the Internet is a powerful tool for controlling and surveilling their citizens, and they have begun enacting common policies for ASes operating within their borders.

  In this paper, we ask how AS topology has changed over time with respect to national boundaries.  We introduce a new measure, \emph{chokepoint potential}, to characterize how a country's AS topology is organized in terms of paths that can carry traffic across international borders.  To study country-level chokepoints, we developed \toolname, a suite of open source, cross platform, and efficient tools for monitoring national chokepoints on the AS graph.  To illustrate these ideas and tools, we studied how chokepoint potential correlates with two independent measures of civil liberty, finding \todo[inline]{NEED A RESULT HERE}. \todo[inline]{NEED A RESULT FOR WHAT WE FOUND FOR EVOLUTION OVER TIME}.

This paper extends earlier research on AS topology and BGP simulation to study chokepoints across the Internet over multiple years, using our
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years. We provide comprehensive and accessible tools for studying
the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible.}

@@

\par Widespread Internet censorship and surveillance pose a
significant threat to individuals throughout the world. As routine
tasks, communications, entertainment, and information move online and
are mediated by the Internet, most of us have little choice about
whether or not to rely on the Internet.  According to the
International Telecommunication Union (ITU), the number of individual
Internet users increased from 1.024 million in 2005 to 3.578 million
in 2017 \cite{itu}. The majority of these users operate in an
environment that restricts Internet freedom in some way. For example,
the 2017 Freedom on the Net report from Freedom House reports that
64\% of Internet users belong to a nation with Internet that is not
free or partly free \cite{FOTN}.  Beyond censorship and surveillance,
the EU is considering content rules surrounding copyright, net
neutrality rules in the U.S.\ were recently overturned, and large
content delivery networks are under enormous pressure to 'do
something' about fake news and bad actors. Taken together, these
trends will likely restructure the Internet in unforeseen ways,
as organizations respond to new challenges and realities.

Today, most such control is exercised at the country level,
as governments have recognized both the threat and the opportunity
that is posed by ubiquitous online communication. For example, much
of the organization, revolutionary momentum, and broadcasting of
events during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}. Several countries
sought to control these movements by disconnecting in-country networks from the rest of the world \todo[inline]{need references here}.

These two factors, increasing levels of content monitoring and
Internet dependence, point to the need for improved tools and methods
for studying worldwide Internet censorship and surveillance over time.
\todo[inline]{A SENTENC OR TWO HERE SUMMARIZING THE STATE OF THE FIELD AND WHAT'S
  MISSING.}  In this paper, we focus on AS-level topology and on
censorship, asking how AS topology has changed over time with respect
to national boundaries.  We define \emph{chokepoint potential} to
quantify how a country’s AS topology is organized in terms of paths
that can carry traffic across international borders.  We developed a
suite of tools, called \toolname, for studying national chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how chokepoint potential correlates with two independent
measures of civilian liberty, finding \todo[inline]{NEED A RESULT HERE}. \todo[inline]{NEED A
  RESULT FOR WHAT WE FOUND FOR EVOLU- TION OVER TIME}.

@@

% Major Contributions
\par
The primary contributions of our work are as follows: 
\begin{enumerate}
 \item We introduce the measure of chokepoint potential and 
motivate its value as way to interpret the capability for a nation to enact censorship of its Internet traffic.
 \item We provide an overview of the evolution of national AS-level chokepoints over time, showing the evolution of the Internet
allowing for a comparision between nations.
 \item We develop a new tool, \toolname, that provides the capability for
efficiently evaluating chokepoints for a given state of the Internet. 
 \item we show that our chokepoint measure
has a significant relationship to Internet freedom as measured by a qualitative source.
\end{enumerate}
